Ensemble Methods for Robust Feature Selection

### 2016-07-12 paper/paper.tex
added poster

\section{Motivation}

Features selection methods is a key method to work with high dimensional data.
It is widely used in areas working with high dimensional data like bioinformatics.
In the past different feature selection methods have been presented.
Additionally, ensemble methods have been presented by \cite{saeys2008}

% Acknowledgements should go at the end, before appendices and references

>>>>

\section{Introduction}

Feature selection is a preprocessing step used in machine learning application to find
a small subset of features in order to build a more accurate, simpler and faster model.
Moreover it allows domain experts to gain a better understanding of the data, by focusing
 on the selected subset.However in domains such as biomedical applications, 
where subsequent analysis are costly, not only the model performance but also the robustness
 of the feature selection method is important. Domain experts would prefer a more stable
 algorithm to have more confidence in the selected features. One approach for more robust
 results are ensemble methods.

In ensemble learning multiple algorithms are combined to obtain better performance or stability.
We build on the work of \cite{saeys2008} who applied ensemble learning by using
the same feature selector on different subsets. In this work we investigate the effect of ensemble methods
further by using multiple feature selection methods. In order to find a good trade-off between robustness
and model performance, multiple feature selection methods were combined in different ways.

\section{Method}
A entropy based measurement. It measures the influence of the class on a feature entropy-wise and normalizes it

We first calculate the weights if avaible by the features selector otherwise the ranks.
For feature selector, which do not omit normalized weights between a0 and 1, we normalize
the weights to the range $[0,1]$. We also normalize the ranks of the features selectors returning
ranks to the range $[0,1]$. Now that we combine the weights after one of the following rules: \ldots

\section{Weaknesses}
- Do SVM\_RFE with exponential rising
- SU achieved high values in the paper, in our results SU weighted a lot of features the 
same; therefore for robustness same weights have to be shuffled to not accidental increase
robustness by order of features
% Acknowledgements should go at the end, before appendices and references
